<meta charset=utf-8>
---
output:
  html_document: default
  pdf_document: default
---
Whitewines Exploring by Erin
========================================================

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
whitewines <- read.csv('wineQualityWhites.csv')
summary(whitewines)
```

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots:quality_barchart}
library(ggplot2)
ggplot(data=whitewines, aes(x = factor(whitewines$quality))) + geom_bar()

```

From the bar chat, we can see most whitewine¡¯s quality is between 5~7,below 5 or above 7 is rare.



```{r echo=FALSE, Univariate_Plots2}
# data structure
str(whitewines)
```

```{r echo=FALSE, Univariate_Plots3}

library(gridExtra)
univ_cont <- function(feature) {
    ggplot(data=whitewines, aes_string(x = feature)) + geom_histogram()
}

quality_hist <- univ_cont("quality")
alcohol_hist <- univ_cont('alcohol')
sulphates_hist <- univ_cont('sulphates')
pH_hist <- univ_cont('pH')
density_hist <- univ_cont('density')
total.sulfur.dioxide_hist <- univ_cont('total.sulfur.dioxide')
free.sulfur.dioxide_hist <- univ_cont('free.sulfur.dioxide')
chlorides_hist <- univ_cont('chlorides')
residual.sugar_hist <- univ_cont('residual.sugar')
citric.acid_hist <- univ_cont('citric.acid')
volatile.acidity_hist <- univ_cont('volatile.acidity')
fixed.acidity_hist <- univ_cont('fixed.acidity')
grid.arrange(quality_hist,alcohol_hist,sulphates_hist,pH_hist,density_hist,
             total.sulfur.dioxide_hist,free.sulfur.dioxide_hist,chlorides_hist,
             residual.sugar_hist,citric.acid_hist,volatile.acidity_hist,
             fixed.acidity_hist,ncol=4)

```

Quality is right skewed, most wines quality is between 5~7,which is normal wine.Bad wine(quality below 5) and good wine(quality above 7) are both rare.
pH,density,total.sulfur.dioxide,chlorides,citric.acid,fixed.acidity looks like normal distribution,alcohol and residual.sugar seems to be unusual,they have different peaks.others are more of rightly skewed poisson distribution.



```{r}
# mean median and quartiles
summary(whitewines[c(2:13)])
```





```{r echo=FALSE, Univariate_Plots4:alcohol_distribution}

summary(whitewines$alcohol)
ggplot(data = whitewines, aes(x = alcohol)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(8,15,0.01)) + 
  labs(x = "alcohol", y = "Count", title = "alcohol")
```

Alcohol distribution is right skewed Poisson distribution.


```{r echo=FALSE, Univariate_Plots5:density_distribution}

summary(whitewines$density)
ggplot(data = whitewines, aes(x = density)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0.98,1.04,0.01)) + 
  labs(x = "density", y = "Count", title = "density")
```

Density distribution is more like a normal distribution.

```{r echo=FALSE, Univariate_Plots6:chlorides_distribution}

summary(whitewines$chlorides)
ggplot(data = whitewines, aes(x = chlorides)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,0.35,.05)) + 
  labs(x = "chlorides", y = "Count", title = "chlorides")
```

Chlorides distribution is more like a normal distribution.


```{r echo=FALSE, Univariate_Plots7:volatile.acidity_distribution}

summary(whitewines$volatile.acidity)
ggplot(data = whitewines, aes(x = volatile.acidity)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0.08,1.10,0.1)) + 
  labs(x = "volatile.acidity", y = "Count", title = "volatile.acidity")
```

Volatile.acidity distribution is right skewed Poisson distribution.


```{r echo=FALSE, Univariate_Plots8:total.sulfur.dioxide_distribution}

summary(whitewines$total.sulfur.dioxide)
ggplot(data = whitewines, aes(x = total.sulfur.dioxide)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(9,450,50)) + 
  labs(x = "total.sulfur.dioxide", y = "Count", title = "total.sulfur.dioxide")
```

Total.sulfur.dioxide distribution is more like a normal distribution.


# Univariate Analysis

### What is the structure of your dataset?
The whitewines dataset has 4898 observations of 13 variables,which the X variable is not a real variable, it's the data record number.

### What is/are the main feature(s) of interest in your dataset?
'quality' is the dependent variable,and the rest 11 variables is the independent variable.The dependent variable 'quality' and independent variables 'alcohol','density','chlorides','volatile.acidity' and 'total.sulfur.dioxide' are the main features of interest.

### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?
From ggpairs we can see there's no significant feature that have strong correlation with 'quality', we need the independent variables together to explore the relationship.

### Did you create any new variables from existing variables in the dataset?
No.
### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?
Quality,alcohol,volatile.acidity are similar, right skewed poisson distribution.Density,chlorides and total.sulfur.dioxide are similar,like normal distribution.The residual.sugar and alcohol distributions are unusual.


```{r echo=FALSE, Univariate_Plots9:residual.sugar_summary}

summary(whitewines$residual.sugar)
```



```{r echo=FALSE, Univariate_Plots10:residual.sugar_distribution}

ggplot(data = whitewines, aes(x = residual.sugar)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,66,5)) +
  labs(x = "residual.sugar", y = "Count", title = "residual.sugar")
```
Residual.sugar distribution is unusual. The left side looks like a normal distribution, while the right side is more like a possion distribution.

```{r echo=FALSE, Univariate_Plots11:residual.sugar_distribution_by_two_parts}

summary(whitewines$residual.sugar)

ggplot(data = whitewines, aes(x = residual.sugar)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(20,66,1)) +
  labs(x = "residual.sugar", y = "Count", title = "residual.sugar~tail")
```


```{r echo=FALSE, Univariate_Plots12:citric.acid_distribution}

summary(whitewines$citric.acid)
ggplot(data = whitewines, aes(x = citric.acid)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,2,.1)) + 
  labs(x = "citric.acid", y = "Count", title = "citric.acid")
```

Citric.acid distribution is more like a normal distribution.But there is a peak left 0.5(citric.acid) and left 0.75(citric.acid).



```{r echo=FALSE, Univariate_Plots13:sulphates_distribution}

summary(whitewines$sulphates)
ggplot(data = whitewines, aes(x = sulphates)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0.22,1.08,0.1)) + 
  labs(x = "sulphates", y = "Count", title = "sulphates")
```

Sulphates distribution is more like a right skewed possion distribution.






# Bivariate Plots Section

```{r fig.width = 15, fig.height = 15,echo=FALSE, Univariate_Plots1:ggpairs}
# use ggpairs to see the overall relationship
library(ggplot2)
library(GGally)
library(scales)
library(memisc)

ggpairs(whitewines[c(2:13)],
  lower = list(continuous = wrap("points", shape = I('.'))),
  upper = list(continuous = wrap("cor", size = 3)))
```

From ggpairs we can see the overall relationship between two variables, and then we can check the variables we care about in details.


```{r echo=FALSE, Bivariate_Plots:alcohol_by_quality}
ggplot(whitewines,aes(factor(quality), alcohol)) + 
  geom_jitter(alpha=0.3) +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red")+
  geom_smooth(method='lm', aes(group = 1))
```

It seems when the alcohol goes up, the quality is increasing(when quality >=5).


```{r echo=FALSE, Bivariate_Plots:quality_vs._alcohol_corr}
cor(x=whitewines$quality,y=whitewines$alcohol,method='pearson')
```




```{r echo=FALSE, Bivariate_Plots:density_vs._alcohol}
ggplot(aes(x = alcohol, y = density), data = whitewines) + 
  geom_point()+ggtitle('Density vs. alcohol')

```

```{r echo=FALSE, Bivariate_Plots:density_vs._alcohol_with_jitter}
ggplot(aes(x = alcohol, y = density), data = whitewines) + 
  geom_point(alpha = 0.25, size = 1, position = 'jitter')+ggtitle('Density vs. alcohol')
```


```{r echo=FALSE, Bivariate_Plots:density_vs._alcohol_with_jitter_move_the_outliters}
ggplot(whitewines,aes(x = alcohol, y = density))+
         scale_x_continuous(lim=c(quantile(whitewines$alcohol,0.01),quantile(whitewines$alcohol,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+ggtitle('Density vs. alcohol')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._alcohol_add_a_linear_line}
ggplot(whitewines,aes(x = alcohol, y = density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$alcohol,0.01),quantile(whitewines$alcohol,0.99)),breaks = c(8, 9, 10, 11,12, 13,14))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs. alcohol')
```


```{r echo=FALSE, Bivariate_Plots:density_vs._alcohol_corr}
cor(x=whitewines$density,y=whitewines$alcohol,method='pearson')
```




```{r echo=FALSE, Bivariate_Plots:density_vs._residual.sugar}
ggplot(aes(x = residual.sugar, y = density), data = whitewines) + 
  geom_point()+ggtitle('Density vs. residual.sugar')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._residual.sugar_with_jitter}
ggplot(aes(x = residual.sugar, y = density), data = whitewines) + 
  geom_point(alpha = 0.08, size = 1, position = 'jitter')+ggtitle('Density vs. residual.sugar')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._residual.sugar_with_jitter_move_the_outliters}
ggplot(whitewines,aes(x = residual.sugar, y = density))+
         scale_x_continuous(lim=c(quantile(whitewines$residual.sugar,0.01),quantile(whitewines$residual.sugar,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+ggtitle('Density vs. residual.sugar')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._residual.sugar_add_a_linear_line}
ggplot(whitewines,aes(x = residual.sugar, y = density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$residual.sugar,0.01),quantile(whitewines$residual.sugar,0.99)),breaks = c(0, 5, 10, 15,20,25))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs. residual.sugar')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._residual.sugar_corr}
cor(x=whitewines$residual.sugar,y=whitewines$density)
```




```{r echo=FALSE, Bivariate_Plots:density_vs._total.sulfur.dioxide}
ggplot(aes(x =  total.sulfur.dioxide, y = density), data = whitewines) + 
  geom_point()+ggtitle('Density vs.  total.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._total.sulfur.dioxide_with_jitter}
ggplot(aes(x =  total.sulfur.dioxide, y = density), data = whitewines) + 
  geom_point(alpha = 1/16, size = 1, position = 'jitter')+ggtitle('Density vs.  total.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._total.sulfur.dioxide_with_jitter_move_the_outliters}
ggplot(whitewines,aes(x =  total.sulfur.dioxide, y = density))+
         scale_x_continuous(lim=c(quantile(whitewines$ total.sulfur.dioxide,0.01),quantile(whitewines$ total.sulfur.dioxide,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+
  geom_point(fill=I('#F79420'),color=I('black'),shape=21)+ggtitle('Density vs.  total.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._total.sulfur.dioxide_add_a_linear_line}
ggplot(whitewines,aes(x =  total.sulfur.dioxide, y = density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$ total.sulfur.dioxide,0.01),quantile(whitewines$ total.sulfur.dioxide,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs.  total.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:density_vs._total.sulfur.dioxide_corr}
cor(x=whitewines$total.sulfur.dioxide,y=whitewines$density)
```

```{r echo=FALSE, Bivariate_Plots:total.sulfur.dioxide_vs._free.sulfur.dioxide}
ggplot(aes(x =  free.sulfur.dioxide, y = total.sulfur.dioxide), data = whitewines) + 
  geom_point()+ggtitle('Total.sulfur.dioxide vs.  Free.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:total.sulfur.dioxide_vs._free.sulfur.dioxide_with_jitter}
ggplot(aes(x =  free.sulfur.dioxide, y = total.sulfur.dioxide), data = whitewines) + 
  geom_point(alpha = 1/16, size = 1, position = 'jitter')+ggtitle('total.sulfur.dioxide vs.  free.sulfur.dioxide')
```


```{r echo=FALSE, Bivariate_Plots:total.sulfur.dioxide_vs._free.sulfur.dioxide_add_a_linear_line}
ggplot(whitewines,aes(x =  free.sulfur.dioxide, y = total.sulfur.dioxide))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$ free.sulfur.dioxide,0.01),quantile(whitewines$ free.sulfur.dioxide,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$total.sulfur.dioxide,0.01),quantile(whitewines$total.sulfur.dioxide,0.99)))+ggtitle('total.sulfur.dioxide vs.  free.sulfur.dioxide')
```

```{r echo=FALSE, Bivariate_Plots:total.sulfur.dioxide_vs._free.sulfur.dioxide_corr}
cor(x=whitewines$free.sulfur.dioxide,y=whitewines$total.sulfur.dioxide)
```
Total.sulfur.dioxide is highly related with free.sulfur.dioxide.So when we create a linear model,we should use one parameter of them.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?
From the above chart,we can see the density rises with residual.sugar increases,while density decreases with alcohol increases.And they are highly related.
### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

Density is highly related with residual.sugar and alcohol.When we keep the residual.sugar constant, the density increase with the alcohol decrease.
Total.sulfur.dioxide is highly related with free.sulfur.dioxide.So when we create a linear model,we should use just one parameter of them.



### What was the strongest relationship you found?

Density vs. residual.sugar, the correlation is almost 0.84.


# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots:density_vs._residual.sugar_colored_by_alcohol}

ggplot(aes(x = residual.sugar, y = density,color=alcohol), data = whitewines) + 
  geom_point(alpha = 0.25, size = 1, position = 'jitter')+ggtitle('Density vs. residual.sugar')
```
Density is highly related with residual.sugar and alcohol.When we keep the residual.sugar constant, the density increase with the alcohol decrease.


```{r echo=FALSE, Multivariate_Plots:density_vs._residual.sugar_colored_by_quality}

ggplot(aes(x = residual.sugar, y = density,color=factor(quality)), data = whitewines) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter')+
  scale_color_brewer(palette = "Blues")+
  ggtitle('Density vs. residual.sugar')
```
Keep the density constant,with residual.sugar increase,the quality increases.

```{r echo=FALSE, Multivariate_Plots:density_vs._alcohol_colored_by_quality}

ggplot(aes(x = alcohol, y = density,color=factor(quality)), data = whitewines) + 
  geom_point(alpha = 0.25, size = 1, position = 'jitter')+
  geom_smooth(method = "lm", se = FALSE,size=1) +
  scale_color_brewer(palette = "Blues") +
  scale_x_continuous() + 
  scale_y_continuous(limits = c(.985,1.005))+
 ggtitle("alcohol by density")+
 ylab("density (g/ml)")+
 xlab("alcohol content (mg/L)")
```

```{r echo=FALSE, Multivariate_Plots:density_vs._total.sulfur.dioxide_colored_by_quality}

ggplot(aes(x = total.sulfur.dioxide, y = density,color=factor(quality)), data = whitewines) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter')+
  scale_color_brewer(palette = "Blues")+
ggtitle('Density vs. total.sulfur.dioxide')
```






```{r echo=FALSE, Multivariate_Plots:linear_model}
m1 <- lm(quality ~ alcohol, data = whitewines)
m2 <- update(m1, ~ . + residual.sugar)
m3 <- update(m2, ~ . + chlorides)

m4 <- update(m3, ~ . + volatile.acidity)

m5 <- update(m4, ~ . + total.sulfur.dioxide)
m6 <- update(m5, ~ . + sulphates)
m7 <- update(m6, ~ . + pH)

mtable(m1, m2, m3, m4, m5, m6, m7)
```



# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

Keep the density constant,with residual.sugar increase,the quality increases.
### Were there any interesting or surprising interactions between features?
Density is highly related with residual.sugar and alcohol.When we keep the residual.sugar constant, the density increase with the alcohol decrease.
### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.
I created a linear model,it proved what I though in the beginning that volatile.acidity and free.sulfur.dioxide have little inflence on quality since when I add them to the linear model,there's almost no change in R-square.But the R-square of the linear model is too little.
------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
# use ggpairs to see the overall relationship
library(gridExtra)
univ_cont <- function(feature) {
    ggplot(data=whitewines, aes_string(x = feature)) + geom_histogram()
}

quality_hist <- univ_cont("quality")+xlab("quality ")
alcohol_hist <- univ_cont('alcohol')+xlab("alcohol content (mg/L)")
sulphates_hist <- univ_cont('sulphates')+xlab("sulphates (g / dm3)")
pH_hist <- univ_cont('pH')+xlab("pH")
density_hist <- univ_cont('density')+xlab("density (mg/L)")
total.sulfur.dioxide_hist <- univ_cont('total.sulfur.dioxide')+xlab("total.sulfur.dioxide content (mg / dm^3)")
free.sulfur.dioxide_hist <- univ_cont('free.sulfur.dioxide')+xlab("free.sulfur.dioxide content (mg / dm^3)")
chlorides_hist <- univ_cont('chlorides')+xlab("chlorides (g / dm^3)")
residual.sugar_hist <- univ_cont('residual.sugar')+xlab("residual.sugar (g / dm^3)")
citric.acid_hist <- univ_cont('citric.acid')+xlab("citric.acid g / dm^3")
volatile.acidity_hist <- univ_cont('volatile.acidity')+xlab("volatile.acidity g / dm^3")
fixed.acidity_hist <- univ_cont('fixed.acidity')+xlab("fixed.acidity g / dm^3")
grid.arrange(quality_hist,alcohol_hist,sulphates_hist,pH_hist,density_hist,
             total.sulfur.dioxide_hist,free.sulfur.dioxide_hist,chlorides_hist,
             residual.sugar_hist,citric.acid_hist,volatile.acidity_hist,
             fixed.acidity_hist,ncol=4)
```

### Description One
From this plot,we can see most whitewine's quality is between 5~7,below 5 or above 7 is rare(about 7.4% of all whitewines)
The dependent variable quality is right skewed,fixed.acidity and PH are roughly normal distributed.Other independent variables are right skewed and have long tail.


### Plot Two
```{r echo=FALSE, Plot_Two}
#install.packages(gridExtra)
library(gridExtra)
p1 <- ggplot(whitewines,aes(x = alcohol, y =      density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$alcohol,0.01),quantile(whitewines$alcohol,0.99)),breaks = c(8, 9, 10, 11,12, 13,14))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs. alcohol')+
 ylab("density (g/ml)")+
 xlab("alcohol content (mg/L)")

p2 <- ggplot(whitewines,aes(x = residual.sugar, y = density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$residual.sugar,0.01),quantile(whitewines$residual.sugar,0.99)),breaks = c(0, 5, 10, 15,20,25))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs. residual.sugar')+
 ylab("density (g/ml)")+
 xlab("residual.sugar (g / dm^3)")

p3 <- ggplot(whitewines,aes(x =  total.sulfur.dioxide, y = density))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$ total.sulfur.dioxide,0.01),quantile(whitewines$ total.sulfur.dioxide,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$density,0.01),quantile(whitewines$density,0.99)))+ggtitle('Density vs.  total.sulfur.dioxide')+
 ylab("density (g/ml)")+
 xlab("total.sulfur.dioxide content (mg / dm^3)")

p4 <- ggplot(whitewines,aes(x =  free.sulfur.dioxide, y = total.sulfur.dioxide))+geom_point(color='#F79420',alpha=1/4)+
  stat_smooth(method='lm')+
         scale_x_continuous(lim=c(quantile(whitewines$ free.sulfur.dioxide,0.01),quantile(whitewines$ free.sulfur.dioxide,0.99)))+
      scale_y_continuous(lim=c(quantile(whitewines$total.sulfur.dioxide,0.01),quantile(whitewines$total.sulfur.dioxide,0.99)))+ggtitle('total.sulfur.dioxide vs.  free.sulfur.dioxide')+
 ylab("total.sulfur.dioxide (mg / dm^3)")+
 xlab("free.sulfur.dioxide (mg / dm^3)")

grid.arrange(p1, p2, p3, p4, ncol=2,
             top = "Scatter plot for the main features ")
```

### Description Two
From this plot we can see that density is highly related with alcohol,residual.sugar and total.sulfur.dioxide,while total.sulfur.dioxide is highly related with free.sulfur.dioxide,but from the first plot, quality is almost no relation with free.sulfur.dioxide, so in the final linear model we can use alcohol,residual.sugar and total.sulfur.dioxide instead of density and free.sulfur.dioxide.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = alcohol, y = density,color=factor(quality)), data = whitewines) + 
  geom_point(alpha = 0.25, size = 1, position = 'jitter')+
  geom_smooth(method = "lm", se = FALSE,size=1) +
  scale_color_brewer(palette = "Blues") +
  scale_x_continuous() + 
  scale_y_continuous(limits = c(.985,1.005))+
 ggtitle("alcohol by density")+
 ylab("density (g/ml)")+
 xlab("alcohol content (mg/L)")

```

### Description Three
With the alcohol constant,the higher density, the better quality. With the density constant, the higher alcohol, the better quality.
------

# Reflection
From univariate part, we can see Quality,alcohol,volatile.acidity are similar, right skewed poisson distribution.Density,chlorides and total.sulfur.dioxide are similar,like normal distribution.The residual.sugar and alcohol distributions are unusual.
From Bivariate Analysis,we can see when the alcohol goes up, the quality is increasing(when quality >=5). The density rises with residual.sugar increases,while density decreases with alcohol increases.And they are highly related.When we keep the residual.sugar constant, the density increase with the alcohol decrease.Total.sulfur.dioxide is highly related with free.sulfur.dioxide.
and density vs. residual.sugar, the correlation is almost 0.84,it's the strongest relationship.
In Multivariate Analysis,when we Keep the density constant,with residual.sugar increase,the quality increases.And density is highly related with residual.sugar and alcohol.When we keep the residual.sugar constant, the density increase with the alcohol decrease.Then I created a linear model,it shows that volatile.acidity and free.sulfur.dioxide have little inflence on quality since when I add them to the linear model,there's almost no change in R-square.But the R-square of the linear model is too little.
In this dataset,the density is highly related with alcohol,residual.sugar and total.sulfur.dioxide,but not that much with quality.While from plot3 we know the quality is related with the combination of density and alcohol.So I use residual.sugar,total.sulfur.dioxide and alcohol to make the linear model instead of density.But the R-square is not good enough.I think this is because the dependent variable quality is somehow ordered caterigorical variable,it's better to use machine learning algorithms like svm or else.